Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-06-04 Submission.Rmd
working on results

Table \@ref(tab:chal-resource-table) summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, challenge stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* < xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation. The total model explained xx% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources explained XX% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a non-significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.

Finally, challenge stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain  and burnout.

```{r hind-resource-table, results='asis'}

@@

papaja::apa_table(regtable,
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
```
We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model. See Table \@ref(tab:ind-resource-table).

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.

Next exploring stress, hindrance stressors and resources explained XX% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. See Figure \@ref(fig:hind-resource-stress-int). As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx. The total model explained xx% of the variance in burnout,$R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. Again, see Figure \@ref(fig:hind-resource-burn-int). As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

>>>>

```{r}
hr_burn_info2 <- apa_print(hr_burn_m2)
hr_burn_info3 <- apa_print(hr_burn_m3)
```

Table \@ref(tab:chal-resource-table) summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)` which represents a statistically significant effect, `r hr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation. The total model explained xx% of the variance in engagement, `r hr_burn_info3$statistic$modelfit$r2` Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources explained XX% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a non-significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.

Finally, challenge stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain  and burnout.

```{r hind-resource-table, results='asis', eval = FALSE}

@@

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model. See Table \@ref(tab:ind-resource-table).

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx. The total model explained xx% of the variance in engagement, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.

Next exploring stress, hindrance stressors and resources explained XX% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation. The total model explained xx% of the variance in stress, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. See Figure \@ref(fig:hind-resource-stress-int). As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx. The total model explained xx% of the variance in burnout,$R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. Again, see Figure \@ref(fig:hind-resource-burn-int). As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources. Papaja gives us `r test$full_result`

### 2024-06-04 Submission.tex
working on results

Outline:
Work toward model (picture)

I. Challenge-hindrance framework
+ Cavanaugh (\textasciitilde2000)
+ Last 20 years' research (variance - look at Pindek et al, 2024)
+ Appraisals \footnote{Ignore JD theory terminology - only talk about JDR \emph{model}, otherwise the verbage becomes confused (4/6/24)}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Antecedents (job elements)
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  O*Net - comprehensive
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Consequences (outcomes)
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Moderation
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Contribution
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  include resources
\end{enumerate}

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes. To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

Cavanaugh et al. (2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.\footnote{Need citations here for hindrance and challenge examples (because subjectivity vs.~``typically a demand'' is a central issue within the paper)}

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even Pindek et al. (2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).\footnote{Citations needed here or alternatively frame the sentence as, ``we contend that\ldots{}''}

Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor\footnote{Do you mean ``stressor'' or ``work characteristic''?} as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} \textless{} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.

@@

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. See Figure \ref{fig:hind-resource-stress-int}. As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between stressors (challenge and hindrance) and outcomes. To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

Cavanaugh et al. (2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict and role ambiguity (M. A. LePine, 2022).

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even Pindek et al. (2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15 which represents a statistically significant effect, \(F(3, 564) = 9.49\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, 2), \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.

@@

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. See Figure \ref{fig:hind-resource-stress-int}. As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources. Papaja gives us \(b = 0.00\), 95\% CI \([-0.08, 0.08]\), \(t(564) = 0.00\), \(p > .999\), \(b = 0.16\), 95\% CI \([0.06, 0.26]\), \(t(564) = 3.10\), \(p = .002\), \(b = 0.03\), 95\% CI \([-0.08, 0.15]\), \(t(564) = 0.56\), \(p = .576\), \(b = -0.13\), 95\% CI \([-0.23, -0.03]\), \(t(564) = -2.63\), \(p = .009\), list(r2 = ``\(R^2 = .05\), 90\textbackslash\% CI \([0.02, 0.08]\), \(F(3, 564) = 9.49\), \(p < .001\)'')
